Enhancement of Speech Recognition Results Using Server-side Post-processing

### 2019-06-30 none_cloud_post_processing_decoding/doc/main.tex
Udpates the paper

\usepackage{neurips_2019}

@@

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

\section{Review on frame-synchronous speech recognition}

\section{The structure of the Server-side Post Processing System}

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. In this figure,  
the two top level blocks on the left and the right hand sides correspond
to {\it speech recognition on the local device} and 
{\it post processing on the server} respectively.  The symbols used in this 
figure is defined as follows:
%
\begin{align}
  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
  on-device speech recognizer.}   \nonumber \\
       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
  y_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
\end{align}
where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
set of words. In Fig. \ref{fig:entire_system}, there are two top level
blocks. The left and right blocks correspond to processing on the local
device and the server side post processing respectively.

\subsection{Label Likelihood Calculation}
To perform decoding described in Section \ref{sec:decoding}, 
we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
label hypothesis.
Using the Bayes rule, this likelihood is expressed in the following form:
\begin{align}
  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
  \label{eq:likelihood_prob}
\end{align}
To calculate the above equation, the following three terms need to be
calculated:
\begin{align}
  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
    \text{ given the frame-synchronous label sequence } \nonumber \\ 
    & \hat{y}_o[0:l+1].
    \nonumber \\
  P\left(\hat{y}_o[0:l+1] \right): & 
    \text{ A probability of the sequence of frame-synchronous labels } \hat{y}_o[0:l+1].
      \nonumber \\
  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
  \label{eq:prob_components_likelihood}
\end{align}

\begin{figure}
    \centering
    \resizebox{30mm}{!}{
      \input{../figures/label_posteior_prob_estimation.tex}
    } 
    \caption {
      Estimation of the label posterior probability
      \label{fig:label_posterior_prob_estimation}
    }
\end{figure}

\section{Introduction}
Recently, there has been tremendous improvements in speech recognition
systems fueled by advances in deep neural networks
\cite{
  Yu2013FeatureLearningDNN, 
  g_hinton_ieee_signal_processing_mag_2012,
  Seltzer2013DNNAurora4, 
  t_sainath_taslp_2017_00,
  t_sainath_book_chapter_2017_00,
  v_vanhoucke_nips_workshop_2011_00}.
TODO(chanw.com) Describes history about starting using DNN, LSTM.

\section{Review on sequence-to-sequence speech recognition algorithms}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.60\textwidth}
    \centering
    \resizebox{78mm}{!}{
      \input{../figures/rnn_t_diagram.tex}
    }
    \caption {
      RNN-T Model.
      \label{fig:rnn_t_diagram}
    }
  \end{subfigure}

  \begin{subfigure}[b]{0.55\textwidth}
    \centering
    \resizebox{53mm}{!}{
      \input{../figures/attention_diagram.tex}
    }
    \caption {
      Attention-based Model.
      \label{fig:attention_diagram}
    }
  \end{subfigure}
  \caption{
    Comparison of block diagrams of different sequence-to-sequence speech
    recognition approaches.
    The proposed Feedback Sequence Classifier (FSC) is shown in 
    Fig. \ref{fig:fsc_diagram}.
  }

@@

>>>>

\usepackage[preprint]{neurips_2019}

@@

\author{
  Chanwoo Kim  \\
  Samsung Research \\
  Seoul, Korea, 06765 \\
  \texttt{chanw.com@samsung.com}  \\
  \And
  Kyungmin Lee  \\
  Samsung Research \\
  Seoul, Korea, 06765 \\
  \texttt{k-m-lee@samsung.com} \\
  \And
  Eunhyang Kim  \\
  Samsung Research \\
  Seoul, Korea, 06765 \\
  \texttt{sc.ehkim.jin@samsung.com} \\
  \And
  Kwangyoun Kim \\
  Samsung Research \\
  Seoul, Korea, 06765 \\
  \texttt{sc.ehkim.jin@samsung.com} \\
  \And
  Dhananjaya Gowda \\
  Samsung Research \\
  Seoul, Korea, 06765 \\
  \texttt{d.gowda@samsung.com} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

Recently, there has been tremendous improvements in speech recognition
systems fueled by advances in deep neural networks
\cite{
  Yu2013FeatureLearningDNN, 
  g_hinton_ieee_signal_processing_mag_2012,
  Seltzer2013DNNAurora4, 
  t_sainath_taslp_2017_00,
  t_sainath_book_chapter_2017_00,
  v_vanhoucke_nips_workshop_2011_00}.
These improvements have come about from the shift from Gaussian Mixture Model
(GMM) to the Feed-Forward Deep Neural Networks (FF-DNNs), FF-DNNs
to Recurrent Neural Network (RNN) and in particular the Long Short-Term Memory
(LSTM) networks.
Thanks to these advances, voice assistant devices such as Google Home
\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
or Amazon Alexa or Samsung Bixby are being used at many homes and on personal devices.

Recently there has been increasing interest in switching
from the conventional Weighted Finite State Transducer (WFST)
based decoder using an Acoustic Model (AM) and a Language Model (LM)
to a complete end-to-end all-neural speech recognition systems
\cite{w_chan_icassp_2016_00, r_prabhavalkar_interspeech_2017_00,
j_chorowski_nips_2015_00}.
These complete end-to-end systems have started surpassing the performance of
the conventional WFST-based decoders with a very large training
database, a better choice of target unit such as Byte Pair Encoded (BPE)
subword units, and an improved training methodology such as Minimum
Word Error Rate (MWER) training.

Another important aspect of these recent improvements in speech
recognition performance is data.
To build high performance speech recognition systems for
conversational speech, we need to use
a large amount of speech data covering various domains. In
\cite{h_soltau_interspeech_2017_00}, it has been shown
that we need a very large training set ($\sim$125,000 hours of
semi-supervised speech data) to achieve
high speech recognition accuracy for difficult tasks like
video captioning. To train neural networks using such large
amounts of speech data, we usually need
multiple Central Processing Units (CPUs) or Graphics
Processing Units (GPUs) or GPU clusters
\cite{E_Variani_INTERSPEECH_2017_01, p_goyal_arxiv_2018_00}.

\section{Overview of the Enhancement by Post-Processing}

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. In this figure,  
the two top level blocks on the left and the right hand sides correspond
to {\it speech recognition on the local device} and 
{\it post processing on the server} respectively.

TODO(chanw.com) Describe the advantage of the server side post-processing.

\begin{subequations}
  \begin{align}
    \text{On-Device Speech Recognition}   : 
        & \quad \{ \, \cdots ,\, \vec{x}[m],     \cdots \, \} \rightarrow  
                \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \} \\
    \text{Server-Side Post-Processing} : 
        & \quad \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \}  \rightarrow
                \{ \, \cdots ,\, W_i,   \cdots \, \}
  \end{align}
\end{subequations}
where $\vec{x}[m]$ is the speech feature vector with $m$ being the 
frame index and $\hat{z}_o[l]$ is the frame-synchronous hypothesis 
from the speech recognizer with $l$ being the frame index. More details
about the frame-synchronous hypothesis will be covered in Sec. 
\ref{sec:frame_synchronous_hypothesis}. The reason for using a different
frame index $l$ for $\hat{z}_o[l]$ is that the frame period in hypothesis
generation may be different from the frame period in feature extraction.
As will be discussed in Sec \ref{sec:frame_synchronous_hypothesis}, 
the sequence of $\hat{z}_o[l]$ is a stream of graphemes.

When the server-side post processing is needed, the sequence of

Before describing structures in detail in Sec.
\ref{sec:frame_synchronous_hypothesis} and in Sec.
\ref{sec:server_side_post_processing}, we will first define notational 
conventions in this section. When representing a sequence consisting of 
periodic elements we will use a bracket symbol to represent elements of
such a sequence. For example, speech features are usually calculated 
periodically at every frame interval (e.g. 10 ms). Thus, we use  
the symbol $\vec{x}[m]$ in
To represent sequences, we will use the bracket symbol
to represent periodic data such as feature vector $\vec{x}[m]$. Usually
speech features are usually sampled at around 10 ms intervals. TODO(chanw.com)
Adds citation. To represent a sequence $\alpha$ starting from the index 
$i$ and ending at $f-1$, we use the notation inspired by the python slice 
notation 
\begin{align}
  \alpha[i:f] = \{ \alpha[m]| i \le m < f \} 
\end{align}
Using this notational convention, we summarize the symbols used in Fig
\ref{fig:entire_system} as follows:
\begin{align}
  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
  on-device speech recognizer.}   \nonumber \\
       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
  y_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
\end{align}
where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
set of words. In Fig. \ref{fig:entire_system}, there are two top level

\section{Obtaining frame-synchronous hypothesis}
\label{sec:frame_synchronous_hypothesis}

In this section, we describe how to obtain frame-synchronous  
hypothesis from a speech recognition decoder.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.50\textwidth}
    \centering
    \resizebox{70mm}{!}{
      \input{../figures/rnn_t_diagram.tex}
    }
    \caption {
      RNN-T Model.
      \label{fig:rnn_t_diagram}
    }
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \resizebox{55mm}{!}{
      \input{../figures/attention_diagram.tex}
    }
    \caption {
      Attention-based Model.
      \label{fig:attention_diagram}
    }
  \end{subfigure}
  \caption{
    Examples of a frame-synchronous decoding in \ref{fig:rnn_t_diagram}
    and a label-synchronous decoding in \ref{fig:attention_diagram}.
  }

@@

\section{The structure of the Server-side Post Processing System}
\label{sec:server_side_post_processing}

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. In this figure,  
the two top level blocks on the left and the right hand sides correspond
to {\it speech recognition on the local device} and 
{\it post processing on the server} respectively.

\subsection{Label Likelihood Calculation}
To perform decoding described in Section \ref{sec:decoding}, 
we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
label hypothesis.
Using the Bayes rule, this likelihood is expressed in the following form:
\begin{align}
  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
  \label{eq:likelihood_prob}
\end{align}
To calculate the above equation, the following three terms need to be
calculated:
\begin{align}
  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
    \text{ given the original frame-synchronous hypothesis } \nonumber \\ 
    & \hat{y}_o[0:l+1].
    \nonumber \\
  P\left(\hat{y}_o[0:l+1] \right): & 
    \text{ A probability of the original frame-synchronous hypothesis } \hat{y}_o[0:l+1].
      \nonumber \\
  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
  \label{eq:prob_components_likelihood}
\end{align}
%
\begin{figure}
    \centering
    \resizebox{40mm}{!}{
      \input{../figures/label_posteior_prob_estimation.tex}
    } 
    \caption {
      Estimation of the label posterior probability
      \label{fig:label_posterior_prob_estimation}
    }
\end{figure}
%
To calculate $P(y_p[l] \big| \hat{y}_o[0:l+1])$ in
\eqref{eq:prob_components_likelihood}, we first train a neural network
to predicting the distribution of $y_p[l]$ given the original 
frame-synchronous hypothesis. Fig. \ref{fig:label_posterior_prob_estimation}
shows the structure of such a neural network stack. To train this
neural network stack, we need to have both the frame-level 
original hypothesis $\hat{y}_o[l]$ and the corresponding the frame-level
ground truth. Since the ground-truth labels are usually not given in the
frame-level format, forced alignment needs to be applied to obtain
the frame-synchronous ground truth.
